%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Marius Hegele} & Email : \href{mailto:marius.hegele@ibmc.om}{marius.hegele@ibm.com}\\
   %\href{http://mariushegele.com/}{mariushegele.com} & Mobile : +49 152 59849858 \\ 
   \href{https://github.com/mariushegele}{github.com/mariushegele} & Mobile : +49 152 59849858 \\
   % \today & Mobile : +49 152 59849858 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Baden-Wuerttemberg Cooperative State University}{Stuttgart, Germany}
      {in cooperation with \textbf{IBM};  current grade: 1.5 (DE)}{Sep. 2017 -- Sep. 2020}
	      \resumeItemListStart
	       	\resumeItem{Mathematical Foundations}
	          {Linear Algebra, Calculus, Stochastic and Combinatorial Optimization}
	         \resumeItem{Other}
	          {Databases, Programming, Software-Engineering}
%	         \resumeItem{Research project}
	%         {Linux kernel hardening}
	      \resumeItemListEnd
	      
    \resumeSubheading
      {University of Würzburg}{Würzburg, Germany}
      {teacher training for subjects English and Mathematics (discontinued)}{Oct. 2016 -- Apr. 2017}
	\resumeSubheading
      {Albertus-Gymnasium}{Lauingen, Germany}
      {Abitur (German A levels), grade: 1.4 (DE)}{Sep. 2007 -- Jun. 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
  	\resumeSubheading
  	{IBM Systems: Functional Hardware Verification}{Böblingen Germany}
  	{Intern Developer}{Jan. 2020 - Sep. 2020}
  	\resumeItemListStart
  	 \resumeItem{\texttt{Python}/\texttt{C++} Interfacing}
  	 {Embedding \texttt{Python} in a \texttt{C++} framework using \texttt{CPython}}
  	 \resumeItem{Integrating with \texttt{Cocotb}}
  	 {\textit{Starting May}}
  	\resumeItemListEnd
  
  	\resumeSubheading
      {IBM Research}{San Jose, USA}
      {Database Research Intern}{Jun. 2019 - Aug. 2019}
      \resumeItemListStart
        \resumeItem{Information Extraction}
          {Extracting features from semi-structured Log Files using \texttt{System T} and Template Mining}
        \resumeItem{Anomaly Detection}
          {Research and comparison of multiple unsupervised approaches to detect anomalies in multivariate, unevenly spaced and categorical data}
      \resumeItemListEnd

    \resumeSubheading
      {IBM Global Business Services}{Hamburg, Germany}
      {Data Science Intern}{Dec. 2018 - Feb. 2019}
      \resumeItemListStart
        \resumeItem{Image Classification}
          {Transfer Learning a Convolutional Neural Network with \texttt{Keras}}
		\resumeItem{Explainable AI}
          {Investigating whether \texttt{LIME} explanations can be used to improve model performance}
      \resumeItemListEnd

    \resumeSubheading
      {IBM Systems: Functional Hardware Verification}{Böblingen, Germany}
      {Intern Build Engineer}{Mar. 2018 -- May 2018}
      \resumeItemListStart
        \resumeItem{Optimization of a verification work flow}
          {Automation and acceleration of a \texttt{Vivado} simulation build using \texttt{GNU Make}}
      \resumeItemListEnd

    \resumeSubheading
    	 {IBM Global Business Services}{Ehningen, Germany}
      {Intern Web-Developer}{Oct. 2017 - Dec 2017}
      \resumeItemListStart
        \resumeItem{Frontend-Development}
          {Development of a RESTful \texttt{Node.js} web application}
        \resumeItem{Scrum and Version Control}
          {Getting to know the Scrum and Kanban methodology; managing a \texttt{Git} workflow}
        \resumeItem{User and Access management}
        {Integrating the w3id SAML SSO}
      \resumeItemListEnd
      
     \resumeSubheading
		{\href{https://www.exone.de}{EXTRA Computer GmbH}}{Sachsenhausen, Germany}
		{Holiday work as computer assembler and warehouse logistician}{Jun. 2017 -- Aug. 2017}     
      
	\resumeSubheading
		{\href{http://mariushegele.com/album-del-viajero/}{Work \& travel gap year}}{South-America}
		{Volunteer and traveller}{Dez. 2015 -- Jun. 2016}
	\resumeItemListStart
        \resumeItem{(Semi-)subsistence agriculture}
          {Planting and harvesting, removing large roots in the valdivian rain forest}
        \resumeItem{Natural building}
          {Construction of a house using mostly renewable resources}
      \resumeItemListEnd
      
	\resumeSubheading
		{\href{https://www.geruestbau-hander.de}{Hander Geruestbau GmbH \& Co. KG}}{Gundelfingen, Germany}
		{Several holiday work periods in construction of scaffolds and warehouse logistics}{Summers 2015, 2016 and 2017}
      

  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{\texttt{Python, Java, C, C++, SQL, Bash}}
    \resumeSubItem{Data Science}{\texttt{NumPy, Pandas, Keras, LIME, MLflow}}
   	\resumeSubItem{Web}{\texttt{JavaScript, Node.js, Angular, Bootstrap}}
	\resumeSubItem{Other}{\texttt{Git, Vim, GNU Make, gcc, Docker}}
  \resumeSubHeadingListEnd

%-----------OTHER-----------------
\section{Other}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {English -- fluent (C1, english study program); \t Spanish -- good (6 months abroad)}
    \resumeSubItem{Volunteering}
      {paramedic in the German Red Cross}
    \resumeSubItem{Hobbies}
      {Basketball, Hiking, Board Games}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}